EqPropNEAT\\Extending NEAT with equlibrium propagation

### 2022-10-09 paper.tex
Expanded the introduction

>>>>

\section{Introduction}
\IEEEPARstart{T}{he} process of designing neural network models always involves deciding on a particular network architecture. In order to avoid both overfitting as well as subpar prediction quality, the right amount of network complexity has to be found for a particular learning task. Over the years, a great amount of experience has accumulated regarding this decision, however these rules are more about empirical know-how, than proven theorems. For our experiment we took well tested and proven algorithms NEAT and Equlibrium Propagation(EQ) and tried to design a neural network which best represents a biological solution to a given task. For this reason EQ was chosen rather than Backpropagation(BP) to further fine tune the network in a way which would be plausible in a biological network. Due to the similarities between BP and EQ we hope to capture all the positive aspects of BP while still maintaining the properties of a biological network. Due to the nature of EQ our networks learns slower than a comparable network would utilizing BP, but as BP is considered "biologically implausible" we accept this shortcoming. In chapter \textbf{N} we will discuss the performance compared to BP and we will explain why the difference in real-world applications would not be significant.
